Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-10 paper/paper_draft.qmd
Update with additional corablox figures

>>>>

![Parametric sensitivity analysis conducted with Shapley effects. Each column reflects
sampling of different DHW ranges. The first column represents model runs with DHW = 0, and
the remaining columns represent models runs with DHW valued between 0 and 8, 8 and 16, 16
and 30, and 0 and 30. The first row shows the Shapley effect for change in coral cover and
the second for change in evenness of species
abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa width fig-align="center"
width="14.82cm"}
